More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
OOPS forgot to commit meeting changes

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$ 
      is 
      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.

 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

@@

%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
%assigned variables.
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are equivalent.

 \end{definition}
Classically, $\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but $\Post_{OT}$ is independent from
$\Post_{OT_x}$), applying the assignments of the involved rules.

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
automata that is an Weak FH-bisimulation and their initial states are equivalent.

@@

       	We will show
       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
       	$(s,u|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s,t_p|\Pred_p)\in\mathcal{R}$,  and 
       	$(t_p,u|\Pred\,'_p)\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation.
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
       	\begin{mathpar}

>>>>

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$ 
      is 
      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.
      \TODO{LudoPred -> Pred s,t}
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

@@

%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
%assigned variables.
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are equivalent.
\TODO{Ludo: define are equivalent : is in the relation les valeurs des variables des 
etats initiaux verifient le predicat associe aux etats initiaux}
 \end{definition}
Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but $\Post_{OT}$ is independent from
$\Post_{OT_x}$), applying the assignments of the involved rules.

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
automata that is an Weak FH-bisimulation and their initial states are equivalent.
\TODO{define equivalent}
 \end{definition}

@@

       	We will show
       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
       	$(s,u|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
       	       	We have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s,t_p|\Pred_p)\in\mathcal{R}$,  and 
       	$(t_p,u|\Pred\,'_p)\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation:
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	\begin{mathpar}
